Sweat electrolytes and CFTR activity in the era of CFTR modulators

### 2025-07-14 Edith Zemanick/Sweat Variability/sweat_test_analysis.qmd
added DOB to sweat tests

    PatientID, Name, Genotypes1, Genotypes2, Sex, Age.at.Test.in.Years,

@@

# For "LESS THAN 10", replace with half the limit of detection
chco[chco == "LESS THAN 10"] <- "9"

@@

    Patient.ID, Patient.Name, Genotype.1, Genotype.2, Sex, Age.at.test..in.years.,
    Sweat.sodium, Sweat.potassium, Sweat.chloride, Sweat.sodium.left.arm,
    Sweat.sodium.right.arm, Sweat.potassium.left.arm, Sweat.potassium.right.arm,
    Sweat.chloride.left.arm, Sweat.chloride.right.arm, Diagnosis

@@

    Name = Patient.Name, Genotypes1 = Genotype.1,

@@

# Change Cl under 10 to 9 per CHEC
df$Cl[df$Cl < 10] <- 9
df$Na[df$Na < 10] <- 9

@@

  select(Name, Diagnosis, Genotypes1, Genotypes2, Sex, Age, Na, K, Cl, `Na:Cl`) %>%

>>>>

    PatientID, Name, DOB, Genotypes1, Genotypes2, Sex, Age.at.Test.in.Years,

@@

# For "LESS THAN 10", replace with missing
chco[chco == "LESS THAN 10"] <- NA

@@

    Patient.ID, Patient.Name, Birth.Date, Genotype.1, Genotype.2,
    Sex, Age.at.test..in.years., Sweat.sodium, Sweat.potassium, Sweat.chloride,
    Sweat.sodium.left.arm, Sweat.sodium.right.arm, Sweat.potassium.left.arm,
    Sweat.potassium.right.arm, Sweat.chloride.left.arm,
    Sweat.chloride.right.arm, Diagnosis

@@

    Name = Patient.Name, Genotypes1 = Genotype.1, DOB = Birth.Date,

@@

# Change Cl under 10 to missing
df$Cl[df$Cl < 10] <- NA
df$Na[df$Na < 10] <- NA

@@

    Name, DOB, Diagnosis, Genotypes1, Genotypes2, Sex, Age, Na, K, Cl, `Na:Cl`
